Alex's Notes and Text Fragments for the JSS Manuscript

### 2022-11-12 paper/article.Rmd
paper: don't exceed page margins with code
style

```{r vis-spcv-non-eval, eval=FALSE}
autoplot(rsmp_sp, task, fold_id = c(1:2), size = 0.8)
```

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_sp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

```{r vis-nspcv-non-eval, eval=FALSE}
autoplot(rsmp_nsp, task, fold_id = c(1:2), size = 0.8)
```

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

>>>>

```{r vis-spcv-non-eval, eval=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.8)
```

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

```{r vis-nspcv-non-eval, eval=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.8)
```

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
